Trans-dimensional Bayesian Inference and Nested Sampling

### 2014-08-11 Documents/Talk/content.tex
Tinkering with layout
Birth death sentence
Dimensions picture
Challenges
Moved slide
Challenges figure slide
NS slide

\begin{frame}[t]{Similarities}
\begin{itemize}
\item Many problems (such as the previous two) have this structure:
\vspace{20pt}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item There are $N$ objects in a region, and we don't know the value of $N$
  \item Each object has properties $\mathbf{x}_i$
  \item We have some data $\mathcal{D}$ which we want to use to infer both $N$
        and $\{\mathbf{x}_i\}_{i=1}^N$.
  \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}[t]{What sampling gives us}
\begin{columns}[T]
\begin{column}{0.4\textwidth}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item {\bf Marginalisation} becomes trivial
  \item We can quantify all uncertainties we might be interested in
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.55\textwidth}
  \includegraphics[scale=0.25]{marginalisation.pdf}
\end{column}

@@

\begin{frame}[t]{Birth and Death}
For problems of unknown dimensionality, the hypothesis space is the union
of several fixed-dimension hypothesis spaces.

>>>>

@@

\begin{frame}[t]{What sampling gives us}
\begin{columns}[T]
\begin{column}{0.35\textwidth}
  \vspace{30pt}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item {\bf Marginalisation} becomes trivial
  \item We can quantify all uncertainties we might be interested in
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.5\textwidth}
  \hspace{-30pt}
  \includegraphics[scale=0.25]{marginalisation.pdf}
\end{column}

@@

\begin{frame}[t]{Structure of the two example problems}
  \begin{itemize}
  \setlength{\itemsep}{10pt}
  \item There are $N$ objects in a region, and we don't know the value of $N$
  \item Each object has properties $\mathbf{x}_i$
  \item We have some data $\mathcal{D}$ which we want to use to infer both $N$
        and $\{\mathbf{x}_i\}_{i=1}^N$.
  \end{itemize}
\begin{center}
\includegraphics[scale=0.5]{../Paper/pgm.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Birth and Death}
For problems of unknown dimensionality, the hypothesis space is the union
of several fixed-dimension hypothesis spaces. Can add {\bf birth and death}
proposals that try to increase or decrease the number of objects in the model.

\begin{figure}
\begin{center}
\includegraphics[scale=0.7]{drawing.pdf}
\end{center}
\end{figure}
\end{frame}

\begin{frame}[t]{What's the issue?}
\begin{itemize}
\setlength{\itemsep}{20pt}
\item Birth-death MCMC seems to have solved our problem. Or has it?
\item What about these challenges?
\vspace{20pt}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item Multiple modes
  \item Strong degeneracies
  \item Phase transitions
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Challenging features}
\begin{center}
\includegraphics[scale=0.4]{challenges.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Nested Sampling}
In 2004, John Skilling introduced {\bf Nested Sampling}, a technique
that starts with the prior distribution, and shrinks volume at a controlled
rate. Maps big space into easy 1-D problem.

Resolves phase transition problem, and helps a little with multiple modes \&
strong degeneracies. Figure from Skilling (2006).

\begin{figure}
\begin{center}
\includegraphics[scale=0.2]{ns.png}
\end{center}
\end{figure}
